Article title

### 2018-10-03 docs/rupee.tex
authors

%TODO
% 1. Subsection 'fast and scalable structure search' is not the final section. 
% 2. In the intro to methods we should indicate the general outline better.

@@

\author{%
Corresponding Author\,$^{1,*}$,
First Co-Author\,$^{2}$
and Second Co-Author\,$^2$%
\footnote{To whom correspondence should be addressed.
Tel: +44 000 0000000; Fax: +44 000 0000000; Email: xxx@yyyy.ac.zz}}

\address{%
$^{1}$Affiliation of Corresponding Author
and
$^{2}$Affiliation of Both Co-Authors}
% Affiliation must include:
% Department name, institution name, full road and district address,
% state, Zip or postal code, country

@@

\subsection{Fast and scalable structure search}

@@

Together, min-hashing and LSH allow for a fast and scalable protein structure search using run position encoded shingles of residue descriptors.

>>>>

@@

\author{%
Ronald Ayoub\,$^{1,}$%
\footnote{To whom correspondence should be addressed.
Email: ronaldayoub@mail.umkc.edu},
Yugyung Lee\,$^{1}$}

\address{%
$^{1}$
School of Computing and Engineering, 
University of Missouri at Kansas City,
5110 Rockhill Road,
Kansas City, MO 64110, USA}

% Affiliation must include:
% Department name, institution name, full road and district address,
% state, Zip or postal code, country

@@

\subsection{Min-hashing and LSH}

@@

Together, min-hashing and LSH provide the foundation for both operating modes of RUPEE, fast and regular.

\subsection{Operating modes}
